High-Dimensional Regularized Discriminant Analysis

### 2013-12-11 reports/paper-hdrda.Rnw
Updated paper to use generic LaTeX template with doublespacing. Removed all AoAS formatting templates. Closes #9

\documentclass[aoas,preprint]{imsart}

\usepackage{graphicx, amsmath, amssymb, bm, mathtools, amsthm}
\RequirePackage[OT1]{fontenc}
\RequirePackage{natbib}
\RequirePackage[colorlinks,citecolor=blue,urlcolor=blue]{hyperref}

% provide arXiv number if available:
%\arxiv{arXiv:0000.0000}

\startlocaldefs
\newcommand{\xbar}{\bar{\bm x}}
\newcommand{\tr}{\text{tr}}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}
\newtheorem{cor}{Corollary}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{thm}{Theorem}
\endlocaldefs

@@

\begin{frontmatter}

\title{High-Dimensional Regularized Discriminant Analysis}
\runtitle{High-Dimensional Regularized Discriminant Analysis}

\begin{aug}
\author{\fnms{John A.} \snm{Ramey}\thanksref{m1}
  \ead[label=e1]{johnramey@gmail.com}
  \ead[label=u1,url]{http://ramhiser.com}}
\author{\fnms{Caleb K.} \snm{Stein}\thanksref{m2}\ead[label=e2]{Caleb\_Stein@baylor.edu}}
\and
\author{\fnms{Dean M.} \snm{Young}\thanksref{m2}\ead[label=e3]{Dean\_Young@baylor.edu}}

\runauthor{J. A. Ramey et al.}

\affiliation{Fred Hutchinson Cancer Research Center\thanksmark{m1} and Baylor University\thanksmark{m2}}

\address{Vaccine and Infectious Disease Division\\
  Fred Hutchinson Cancer Research Center\\
  1100 Fairview Ave. N., M2-C200\\
  Seattle, Washington 98115, U.S.A.\\
  \printead{e1}\\
  \printead{u1}}

\address{Department of Statistical Science\\
  Baylor University\\
  P.O. Box 97140\\
  Waco, Texas 76706, U.S.A.\\
  \printead{e2}\\
  \phantom{E-mail:\ }\printead*{e3}}
\end{aug}

@@

\begin{keyword}
\kwd{classification}
\kwd{regularized discriminant analysis}
\kwd{covariance-matrix regularization}
\kwd{high-dimensional multivariate analysis}
\kwd{microarray data}
\end{keyword}

\end{frontmatter}

@@

Several regularization methods, such as the methods considered by
\citet*{Guo:2007te}, \cite{Mkhadri:1995jp}, and \citet*{Xu:2009fl}, have been
proposed in the literature to adjust the eigenvalues of $\widehat{\bm \Sigma}_k$
so that \eqref{eq:qda} is calculable and has reduced variability in the standard
bias-variance tradeoff. A common form of the covariance-matrix regularization
applies a shrinkage factor $\gamma > 0$, so that
\begin{align}
	\widehat{\bm \Sigma}_k(\gamma) =  \widehat{\bm \Sigma}_k + \gamma \bm I_p, \label{eq:ridge-estimator}
\end{align}
similar to a method employed in ridge regression \citep{Hoerl:1970cd}. Equation
\eqref{eq:ridge-estimator} effectively \emph{shrinks} the sample covariance
matrix $\widehat{\bm \Sigma}_k$ toward $\bm I_p$, thereby increasing the
eigenvalues of $\widehat{\bm \Sigma}_k$ by $\gamma$. Specifically, the zero
eigenvalues are replaced with $\gamma$, so that \eqref{eq:ridge-estimator} is
positive definite. For additional covariance-matrix regularization methods, see
\cite{Ramey:2013ji}, \cite{Xu:2009fl}, and \cite{Ye:2009gd}.

@@

Thus, by incorporating each $\bm x_i$ into the estimation of $\bm \Sigma_k$, we
increase the rank of $\widehat{\bm \Sigma}_k(\lambda)$ to $q$ if $\lambda \ne
0$. Next, we provide an essential result that enables us to prove that
\eqref{eq:hdrda} is invariant to adjustments to the eigenvalues of $\tilde{ \bm
  \Sigma}_k$ corresponding to the null space of $\widehat{\bm \Sigma}$ for any
unlabeled observation $\bm x \in \mathbb{R}_{p \times 1}$.

@@

\begin{supplement}
\sname{Supplement A}\label{suppA}
\stitle{R Package Containing Microarray Data Sets}
\slink[url]{https://github.com/ramey/datamicroarray}
\sdescription{An R package containing all of the microarray data sets used in
  the classification study.}
\end{supplement}

\begin{supplement}
\sname{Supplement B}\label{suppB}
\stitle{Optimal Estimates of the HDRDA Classifier}
\slink[url]{https://github.com/ramey/paper-hdrda/tree/annals-of-applied-statistics/reports}
\sdescription{The graphical summary of the optimal estimates of the \emph{HDRDA} classifier from the classification study.}
\end{supplement}

\bibliographystyle{imsart-nameyear}
\bibliography{rda}

>>>>

\documentclass{article}

\usepackage{graphicx, amsmath, amssymb, bm, mathtools, amsthm}
\usepackage{natbib, setspace}

\newcommand{\xbar}{\bar{\bm x}}
\newcommand{\tr}{\text{tr}}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}
\newtheorem{cor}{Corollary}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{thm}{Theorem}

@@

\title{High-Dimensional Regularized Discriminant Analysis}

\author{John A. Ramey, Caleb K. Stein, \and Dean M. Young}

\maketitle

\doublespacing

@@

@@

Several regularization methods, such as the methods considered by
\citet*{Xu:2009fl}, \citet*{Guo:2007te}, and \cite{Mkhadri:1995jp} have been
proposed in the literature to adjust the eigenvalues of $\widehat{\bm \Sigma}_k$
so that \eqref{eq:qda} is calculable and has reduced variability in the standard
bias-variance tradeoff. A common form of the covariance-matrix regularization
applies a shrinkage factor $\gamma > 0$, so that
\begin{align}
	\widehat{\bm \Sigma}_k(\gamma) =  \widehat{\bm \Sigma}_k + \gamma \bm I_p, \label{eq:ridge-estimator}
\end{align}
similar to a method employed in ridge regression \citep{Hoerl:1970cd}. Equation
\eqref{eq:ridge-estimator} effectively \emph{shrinks} the sample covariance
matrix $\widehat{\bm \Sigma}_k$ toward $\bm I_p$, thereby increasing the
eigenvalues of $\widehat{\bm \Sigma}_k$ by $\gamma$. Specifically, the zero
eigenvalues are replaced with $\gamma$, so that \eqref{eq:ridge-estimator} is
positive definite. For additional covariance-matrix regularization methods, see
\cite{Ramey:2013ji}, \cite{Xu:2009fl}, and \cite{Ye:2009gd}.

@@

Thus, by incorporating each $\bm x_i$ into the estimation of $\bm \Sigma_k$, we
increase the rank of $\widehat{\bm \Sigma}_k(\lambda)$ to $q$ if $\lambda \ne
0$. The results is that the \emph{HDRDA} classifier has the advantage over
\eqref{eq:qda} in that the rank$(\widehat{\bm \Sigma}_k) \le n_k$. Next, we
provide an essential result that enables us to prove that \eqref{eq:hdrda} is
invariant to adjustments to the eigenvalues of $\tilde{ \bm \Sigma}_k$
corresponding to the null space of $\widehat{\bm \Sigma}$ for any unlabeled
observation $\bm x \in \mathbb{R}_{p \times 1}$.

@@

\bibliographystyle{plainnat}
\bibliography{rda}
